---
title: "DATA607 Final Project"
author: "Javern Wilson"
date: "May 8, 2019"
output: html_document
---


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(reshape2)
library(kableExtra)
library(rvest)
library(XML)
library(RCurl)
library(tm)
library(pdftools)

```
## Import and Clean

At first the [Air_Quality](https://github.com/javernw/DATA607GroupProjects/blob/master/Final%20Project/Air_Quality.csv) data is read into R. Any rows that are not completed is removed. For this project, we will only focus on the boroughs and the neighborhoods within. UHF42
```{r}

air_quality <- read.csv("https://raw.githubusercontent.com/javernw/DATA607GroupProjects/master/Final%20Project/Air_Quality.csv", header = T) #Air_Quality.csv
air_q <- air_quality #use a secondary variable for analysis
air_q <- air_q[complete.cases(air_q), ] #only keep full rows

#columns not needed for analysis is removed
air_q <- air_q %>%  select(-indicator_data_id, -indicator_id, -year_description)
air_q <- filter(air_q, geo_type_name == c("Borough", "UHF42"))


```

Categories considered when analysing air quality.
```{r}
airq_cat <- air_q %>% select(name) %>% distinct()

kable(airq_cat) %>% kable_styling(bootstrap_options = "striped" ,font_size = 12) %>% scroll_box(height = "500px")

```

Collect Zipcode and Matching Neighborhood with UHF42 Code
```{r}
link <- "https://www.health.ny.gov/statistics/cancer/registry/appendix/neighborhoods.htm"

zip_table <- link %>% read_html() %>% html_nodes("table") %>% html_table(fill = T) %>% data.frame(stringsAsFactors = F)

#add UHF42 code column
zip_table$NCode <- c(105, 103, 106, 107, 101, 102, 104, 203, 209, 206, 208, 210, 202, 207, 204, 201, 205, 211, 302, 306, 303, 307, 308, 310, 309, 305, 304, 301, 404, 403, 406, 408, 401, 405, 410, 409, 407, 402, 501, 503, 502, 504)

#re-arrange columns
zip_table <- zip_table[, c(1,4,2,3)]

```

Collect Rent Prices for each Neighborhood and Borough

```{r eval=FALSE, include=FALSE}

### Bronx

bronx_url<-paste0("https://www.apartments.com/bronx-ny/", 1:20)

bronx <- lapply(bronx_url,
                function(pg){
                  pg %>% read_html() %>% 
                    html_nodes("#placards") %>% 
                    html_text() %>%
                    str_extract_all("\\$\\d.\\d+")
                })
bronx <- parse_number(unlist(bronx))

Bxurl1 <- "https://www.apartments.com/mount-hope-bronx-ny/"
central_bronx <- Bxurl1 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Bxurl2 <- "https://www.apartments.com/fordham-heights-bronx-ny/"
fordham <- Bxurl2 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Bxurl3 <- "https://www.apartments.com/highbridge-bronx-ny/"
high_bridge <- Bxurl3 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()%>% mean()

Bxurl4 <- "https://www.apartments.com/mount-hope-bronx-ny/"
huntspoint <- Bxurl4 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Bxurl5 <- "https://www.apartments.com/kingsbridge-bronx-ny/"
kingsbridge <- Bxurl5 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Bxurl6 <- "https://www.apartments.com/mount-hope-bronx-ny/"
north_eastbx <- Bxurl6 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Bxurl7 <- "https://www.apartments.com/parkchester-bronx-ny/"
south_eastbx <- Bxurl7 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()


####Brooklyn


brooklyn_url<-paste0("https://www.apartments.com/brooklyn-ny/", 1:20)

brooklyn <- lapply(brooklyn_url,
                function(pg){
                  pg %>% read_html() %>% 
                    html_nodes("#placards") %>% 
                    html_text() %>%
                    str_extract_all("\\$\\d.\\d+")
                })
brooklyn <- parse_number(unlist(brooklyn))

Burl1 <- "https://www.apartments.com/crown-heights-brooklyn-ny/"
central_brooklyn <- Burl1 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number() %>% mean()

Burl2 <- "https://www.apartments.com/southwest-brooklyn-brooklyn-ny/"
sw_brooklyn <- Burl2 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Burl3 <- "https://www.apartments.com/borough-park-brooklyn-ny/"
borough_park <- Burl3 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Burl4 <- "https://www.apartments.com/flatlands-brooklyn-ny/"
canarsie_flatlands <- Burl4 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Burl5 <- "https://www.apartments.com/coney-island-brooklyn-ny/"
south_brooklyn <- Burl5 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Burl6 <- "https://www.apartments.com/park-slope-brooklyn-ny/?bb=62kx98lnvHihhqwB"
nw_brooklyn <- Burl6 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Burl7 <- "https://www.apartments.com/flatbush-brooklyn-ny/"
flatbush <- Burl7 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Burl8 <- "https://www.apartments.com/east-new-york-brooklyn-ny/"
east_ny <- Burl8 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Burl9 <- "https://www.apartments.com/greenpoint-brooklyn-ny/"
greenpoint <- Burl9 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Burl10 <- "https://www.apartments.com/sunset-park-brooklyn-ny/"
sunset_park<- Burl10 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Burl11 <- "https://www.apartments.com/bushwick-brooklyn-ny/"
bushwick <- Burl11 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()




#### Manhattan

manhattan_url <-paste0("https://www.apartments.com/brooklyn-ny/", 1:20)

manhattan <- lapply(manhattan_url,
                function(pg){
                  pg %>% read_html() %>% 
                    html_nodes("#placards") %>% 
                    html_text() %>%
                    str_extract_all("\\$\\d.\\d+")
                })
manhattan <- parse_number(unlist(manhattan))

Murl1 <- "https://www.apartments.com/central-harlem-new-york-ny/"
central_harlem <- Murl1 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Murl2 <- "https://www.apartments.com/chelsea-new-york-ny/"
chelsea_clinton <- Murl2 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Murl3 <- "https://www.apartments.com/east-harlem-new-york-ny/"
east_harlem <- Murl3 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Murl4 <- "https://www.apartments.com/gramercy-park-new-york-ny/"
gramercy_murray <- Murl4 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Murl5 <- "https://www.apartments.com/greenwich-village-new-york-ny/"
greenwich_soho <- Murl5 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Murl6 <- "https://www.apartments.com/lower-manhattan-new-york-ny/"
lower_manhattan <- Murl6 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Murl7 <- "https://www.apartments.com/lower-east-side-new-york-ny/"
lower_east <- Murl7 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Murl8 <- "https://www.apartments.com/upper-east-side-new-york-ny/"
upper_east <- Murl8 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Murl9 <- "https://www.apartments.com/upper-west-side-new-york-ny/"
upper_west <- Murl9 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Murl10 <- "https://www.apartments.com/washington-heights-new-york-ny/"
inwood_washington <- Murl10 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

### Queens

queens_url <-paste0("https://www.apartments.com/queens-ny/", 1:20)

queens <- lapply(queens_url,
                function(pg){
                  pg %>% read_html() %>% 
                    html_nodes("#placards") %>% 
                    html_text() %>%
                    str_extract_all("\\$\\d.\\d+")
                })
queens <- parse_number(unlist(queens))

Qurl1 <- "https://www.apartments.com/northeast-queens-flushing-ny/"
north_east <- Qurl1 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Qurl2 <- "https://www.apartments.com/bayside-ny/"
north <- Qurl2 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Qurl3 <- "https://www.apartments.com/central-queens-queens-ny/"
central <- Qurl3 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Qurl4 <- "https://www.apartments.com/southeast-queens-jamaica-ny/"
jamaica <- Qurl4 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Qurl5 <- "https://www.apartments.com/long-island-city-ny/"
north_west <- Qurl5 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Qurl6 <- "https://www.apartments.com/forest-hills-ny/"
west_central <- Qurl6 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Qurl7 <- "https://www.apartments.com/south-shore-queens-far-rockaway-ny/"
rockaway <- Qurl7 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Qurl8 <- "https://www.apartments.com/hollis-ny/"
south_east <- Qurl8 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Qurl9 <- "https://www.apartments.com/howard-beach-ny/"
south_west <- Qurl9 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Qurl10<- "https://www.apartments.com/northeast-queens-flushing-ny/"
west <- Qurl10 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()



#### Staten Island

SI_url <-paste0("https://www.apartments.com/staten-island-ny/", 1:20)

Staten_Island <- lapply(SI_url,
                function(pg){
                  pg %>% read_html() %>% 
                    html_nodes("#placards") %>% 
                    html_text() %>%
                    str_extract_all("\\$\\d.\\d+")
                })
Staten_Island <- parse_number(unlist(Staten_Island))

Surl1 <- "https://www.apartments.com/port-richmond-staten-island-ny/"
port_richmond <- Surl1 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Surl2 <- "https://www.apartments.com/stapleton-staten-island-ny/"
stapleton <- Surl2 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Surl3 <- "https://www.apartments.com/staten-island-ny-10306/"
south_shore <- Surl3 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()

Surl4 <- "https://www.apartments.com/staten-island-ny-10314/"
mid_island <- Surl4 %>% read_html() %>%  html_node("#placards") %>%
    html_text() %>% str_extract_all("\\$\\d.\\d+") %>% unlist() %>% parse_number()%>% mean()


```


```{r}



```


Collect Neighborhood and Matching UHF42 Code from pdf file on web
```{r}
file <- 'http://a816-dohbesp.nyc.gov/IndicatorPublic/EPHTPDF/uhf42.pdf'


text <- pdf_text(file)
text2 <- strsplit(text, "\n")
uhf42_codes <- text2 %>% 
  str_extract_all(pattern = "\\d{3}") %>% 
  unlist() %>% 
  parse_number() %>% 
  unique() %>% 
 sort()
  

uhf42_names <- gsub("NYC UHF 42 Neighborhoods", "", text2)
uhf42_names <- gsub("UHF Neighborhood Name", "", uhf42_names)
uhf42_names <- gsub("UHF Code", "", uhf42_names)
uhf42_names <- gsub("Neighborhood Definition:.+", "", uhf42_names)
uhf42_names <- gsub("\\d{3}", "", uhf42_names)
uhf42_names <- unlist(str_extract_all(uhf42_names, "(\\s[A-Za-z]+.\\-?.[A-Za-z]+.\\-?.[A-Za-z]+.[A-Za-z]+.\\-?.[A-Za-z]+| Jamaica| Rockaway| Sunset Park)"))
uhf42_names <- gsub("\\\\r", "", uhf42_names)

neighborhood <- data.frame(Code = uhf42_codes, Location = uhf42_names, stringsAsFactors = F)

#write.csv(neighborhood, file = "Neighborhood.csv", row.names = F)

```

UHF42 Codes and Rent Prices

```{r}
Rent_prices <- c(central_bronx, fordham, high_bridge, huntspoint, kingsbridge, north_eastbx, south_eastbx, central_brooklyn, sw_brooklyn, borough_park, canarsie_flatlands, south_brooklyn, nw_brooklyn, flatbush, east_ny, greenpoint, sunset_park, bushwick, central_harlem, chelsea_clinton, east_harlem, gramercy_murray, greenwich_soho, lower_manhattan, lower_east, upper_east, upper_west, inwood_washington, north_east, north, central, jamaica, north_west, west_central, rockaway, south_east, south_west, west, port_richmond, stapleton, south_shore, mid_island)

rent <- data.frame(UHF42Code = zip_table$NCode, avg_Rentprice = Rent_prices, stringsAsFactors = F)

#write.csv(rent, file = "Rent.csv", row.names = F) #store file

```

Create new data table
```{r}

air_rent <- inner_join(air_q, rent, by = c("geo_entity_id" = "UHF42Code"))

#write.csv(air_rent, file = "Air_Rent.csv", row.names = F)

```

